Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-03-16 ms/ms.Rnw
playing with figures

<<panel3>>=

@ 
\begin{itemize}
\item Time plot (3-panel plot): baseline dynamics, illustrating summary statistics (peak time, eq virulence, length of time until peak virulence). Full Shirreff model, effects of $I(0)$, $\alpha(0)$, $r$
\item Virulence trajectories under all models
\item Univariate plots
\item Bivariate plots
\item Unscaled sensitivity 
\end{itemize}

@@

>>>>

<<panel3,fig.cap="Baseline dynamics. Time series of mean population virulence ($\\log_{10}$ SPVL). (a) Shirreff model, effects of varying $r$. (b) Effects of varying initial infectious density $I(0)$. (c) Effects of varying initial mean virulence $\\alpha(0)$",dev="tikz",fig.height=3,fig.width=8,cache=TRUE>>=
for (i in c("","2","3")) 
    load(sprintf("../simdata/ev_LHS_resS%s.rda",i))
Ls <- load("../simdata/shirreff_data.rda")
tvec <- seq(from=1,by = 0.1,length.out=nrow(vir_matS))
dimnames(vir_matS) <- list(Time=tvec,
                           run=paste0("$r=",c(0.021,0.042,0.084),"$"))

d_littleR_m <- melt(vir_matS,value.name="Mean.VL")
shirreff_df_m <- subset(res_sum_df,run==1,select=c(run,Time, Mean.VL))
shirreff_df_m$run <- "Shirreff"
df_tot <- rbind(shirreff_df_m,d_littleR_m)
vlab <- "mean virulence ($\\log_{10}$ SPVL)"
tlab <- "time (years)"
g1 <- ggplot(df_tot,aes(x=Time,y=Mean.VL,colour=run))+
    geom_line()+labs(x=tlab,y=vlab)+
    theme(legend.position=c(0.8,0.2))
###
dimnames(vir_matS2) <- list(Time=tvec,
               run=c("$10^{-3}$", "$10^{-4}$", "$10^{-5}$"))
g2 <- g1 %+% melt(vir_matS2,id.var="Time",value.name="Mean.VL")
###
dimnames(vir_matS3) <- list(Time=tvec,
                            run=c("$2.5$", "$3$", "$3.5$"))
g3 <- g1 %+% melt(vir_matS3,id.var="Time",value.name="Mean.VL")
limits <- c(2.5,4.7)
breaks <- seq(limits[1],limits[2], by = 0.5)
g1.y <- g1 + scale_y_continuous(limits = limits, breaks = breaks)+
    scale_colour_discrete(name="run")
g2.y <- g2 + scale_y_continuous(limits = limits, breaks = breaks)+
    scale_colour_discrete(name="$I(0)$")
g3.y <- g3 + scale_y_continuous(limits = limits, breaks = breaks)+
        scale_colour_discrete(name="$\\alpha(0)$")
grid.arrange(g1.y, g2.y, g3.y, nrow=1)
@

<<virtraj,fig.cap="Envelopes of virulence trajectories under all models",dev="tikz",fig.width=6,cache=TRUE>>=
gg_virtraj <- ggplot(sum_list[["vir_mat"]],
       aes(tvec,mean,ymin=lwr,ymax=upr))+
    geom_line(aes(colour=model,linetype=model),lwd=1.5)+
    geom_ribbon(aes(fill=model),alpha=0.3)+
    labs(x="time",y=vlab)
print(gg_virtraj)
@

<<unidist,fig.cap="Univariate distributions of summary statistics. Note: point for eqvir/random is a placeholder, will have to be explained",fig.width=8,fig.height=4.8>>=
sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
mL <- melt(sL,id.vars=c("model","run"))
## horrible hack (but doesn't help); subsample
## w <- which(mL$model=="random")
## mLw <- mL[-sample(w,size=length(w)*9/10,replace=FALSE),]
w <- with(mL,which(model=="random" & variable=="eq_vir"))
rval <- mean(mL$value[w])
mLw <- droplevels(mL[-w,])
ggplot(mLw,aes(value,model,fill=model))+
    geom_violinh(width=1)+
    facet_wrap(~variable,scale="free_x")+
    guides(fill=guide_legend(reverse=TRUE))+
    labs(y="")+
    geom_point(data=data.frame(model="random",variable="eq_vir",
                               value=rval),pch=22,size=3,show.legend=FALSE)
@

<<testrev,echo=FALSE,eval=FALSE>>=
set.seed(101)
zz <- data.frame(x=rnorm(3000),f=factor(rep(letters[1:3],each=1000)))
g0 <-  ggplot(zz,aes(x=f,y=x,fill=f))+geom_violin()
grid.arrange(
    g0,
    g0+ guides(fill=guide_legend(reverse=TRUE)),
    nrow=2)
@

Figure to-do:
\begin{itemize}
\item fig 1. add labels? tweak size? remove redundant y axes?
\item fig 3. add random-mixing model
\item fig 4. re-order (reverse legend order), figure out how to tweak random density width
\end{itemize}

\begin{itemize}
\item Univariate plots
\item Bivariate plots
\item Unscaled sensitivity 
\end{itemize}

@@

\todo{explain non-standard use of Kronecker delta as exponent!}
